The Strong Gravitational Lens Finding Challenge

### 2017-05-15 paper.tex
Added “All” method section.

\author[R. B. Metcalf {\it et al.}]{
R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
M. Meneghetti,$^4$ 
Fabio Bellagamba,$^1$
Emmanuel Bertin,$^3$ 
\newauthor
R\'emi Cabanac,$^2$ 
Etienne Decenci\`ere,$^{10}$
Remi Flamary,$^8$
Mario Geiger,$^6$ 
\newauthor
Philippa Hartley,$^7$
Marc Huertas-Company,$^9$
Neal Jackson,$^7$ 
Jean-Paul Kneib,$^6$
\newauthor
Christoph Sch\"{a}fer,$^6$ 
Alessandro Sonnenfeld,$^5$ 
Amit Tagore,$^7$
Diego Tuccillo,$^{9,10}$
\newauthor
Santiago Velasco-Forero,$^{10}$
and ?\\
% List of institutions
$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
$^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
$^{3}$ Sorbonne Universit\'{e}s, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  98bis Bd Arago, F-75014,\\ Paris France.\\
$^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
$^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{6}$ \red{EPFL}\\
$^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of Manchester, Oxford Rd, Manchester M13 9PL, UK \\
$^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique, Observatoire de la C\^{o}te d'Azur, \\ Parc Valrose, 06108 Nice, France \\
$^{9}$ LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France \\
$^{10}$ Centre for mathematical morphology, Mathematics and Systems department, MINES ParisTech, 35 rue Saint-Honore, Fontainebleau, France \\
}

@@

@@

EB thanks Raphael Gavazzi for proposing him to participate to the challenge.
AS was supported by World Premier International Research Center Initiative (WPI Initiative), MEXT, Japan.
RBM's research was partly part of project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n. 259349.
AT acknowledges receipt of an STFC postdoctoral research
assistantship.
\red{We thank the International Space Science Institute (ISSI) for hosting and funding our workshop.\footnote{http://www.issibern.ch/}}

>>>>

\author[R. B. Metcalf {\it et al.}]{
R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
M. Meneghetti,$^4$ 
Fabio Bellagamba,$^1$
Emmanuel Bertin,$^3$ 
\newauthor
R\'emi Cabanac,$^2$ 
Etienne Decenci\`ere,$^{10}$
Remi Flamary,$^8$
Mario Geiger,$^6$ 
\newauthor
Philippa Hartley,$^7$
Marc Huertas-Company,$^9$
Neal Jackson,$^7$ 
Jean-Paul Kneib,$^6$
\newauthor
Christoph Sch\"{a}fer,$^6$ 
Alessandro Sonnenfeld,$^5$ 
Amit Tagore,$^7$
Diego Tuccillo,$^{9,10}$
\newauthor
Santiago Velasco-Forero,$^{10}$
Camille Avestruz,$^{11-13,\dagger}$
Nan Li,$^{12-14}$
Matthew Lightman,$^{15}$
\newauthor
and ?\\
% List of institutions
$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
$^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
$^{3}$ Sorbonne Universit\'{e}s, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  98bis Bd Arago, F-75014,\\ Paris France.\\
$^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
$^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{6}$ \red{EPFL}\\
$^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of Manchester, Oxford Rd, Manchester M13 9PL, UK \\
$^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique, Observatoire de la C\^{o}te d'Azur, \\ Parc Valrose, 06108 Nice, France \\
$^{9}$ LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France \\
$^{10}$ Centre for mathematical morphology, Mathematics and Systems department, MINES ParisTech, 35 rue Saint-Honore, Fontainebleau, France \\
$^{11}${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^{12}${Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^{13}${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^{14}${High Energy Physics Division, Argonne National Laboratory, Lemont, IL 60439}\\
$^{15}${JPMorgan Chase, Chicago, IL 60603 U.S.A.}\\
$^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
}

@@

%-------------------------------------------------%
\subsection{ALL Methodology (Avestruz, Li, Lightman}
%-------------------------------------------------%

We detail the ALL team methodology in \citet{avestruz_etal17}. The
pipeline was originally developed to automatically classify strong
lenses in mock Hubble Space Telescope and Large Synoptic Sky Telescope
data generated with code described in \citet{li_etal16} and
\citet{collett_15}.  We apply the same exact steps for the single-band
data for Euclid, but modify the feature extraction step for the
four-band KIDS data.  We summarize the steps below.

We use tools from {\em Scikit-learn} \citep{pedregosa_etal12} and
perform minimal image preprocessing. First, we replace masked pixels
with the average of surrounding pixels, then enhance contrast in the
image by taking the normalized log of pixel values.  The next step of
our pipeline consists of a feature extraction stage, where our feature
vector is a {\em histogram of oriented gradients} (HOG)
\citep{dalalandtriggs_05} that quantifies edges in the image.  HOG has
three main parameters that determine the binning and resolution of
edges captured by the features.  The result is a one dimensional
feature vector corresponding to the magnitude of oriented gradients
across the image.  With the KIDS data, we extract a feature vector for
each of the four bands and concatenate the vectors to create a final
feature vector for each object that we use to train a model
classifier.

We use {\em Logistic Regression} (LR), a machine learning algorithm,
to train a classifier model.  LR requires a parameter search over the
regression coefficient, $C_{LogReg}$.  The parameters from both the
feature extrator, HOG, and the linear classifier, LR, contain
parameters that we optimize for peak model performance.  We use {\em
  GridSearchCV} from {\em Scikit-learn} to select cross-validated
parameters for HOG parameters and a subset of $C_{LogReg}$ values with
20\% of the test images provided.  We then run a finer parameter
search over $C_{LogReg}$, splitting the test images into 80\% training
and and 20\% test to avoid overfitting the data.  We use the best
parameters to then train the entire dataset for the final model
classifier that we used to evaluate the competition data.

@@

EB thanks Raphael Gavazzi for proposing him to participate to the challenge.
AS was supported by World Premier International Research Center Initiative (WPI Initiative), MEXT, Japan.
RBM's research was partly part of project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n. 259349.
AT acknowledges receipt of an STFC postdoctoral research
assistantship.
\red{We thank the International Space Science Institute (ISSI) for hosting and funding our workshop.\footnote{http://www.issibern.ch/}}
CA acknowledges support from the Enrico Fermi
Institute at the University of Chicago, and the University of Chicago
Provost's Office. NL would like to thank the funding support from
NSFC, grant no.11503064, and Shanghai Natural Science Foundation,
grant no. 15ZR1446700. This work was also supported in part by the
Kavli Institute for Cosmological Physics at the University of Chicago
through grant NSF PHY-1125897 and an endowment from the Kavli
Foundation and its founder Fred Kavli.
